Implementation Design Patters for Pursuit-Evasion Problems with Bounded Speed

### 2012-11-30 paper.tex
finalized discrete formulation

\usepackage{amsmath}

@@

Provided that \(G\) is a planar graph, we can make the assumption that we will only need at most three pursuers to catch all evaders. \cite{copsRobbers} We can show this with the following algorithm:

>>>>

\usepackage{amsmath}
\usepackage{algorithm2e}

@@

Provided that \(G\) is a planar graph, we can make the assumption that we will only need at most three pursuers to catch all evaders, as proven by Aigner and Fromme. This is performed by one to three pursuers sequentially closing off the region occupied by an evader, tackling each one at a time. One pursuer is able to step into the area where the evader is free to move, and its cohorts (if any) are able to cover its congruent spaces, taking advantage of the planar properties of the graph. This is repeated until each evader is caught. \cite{copsRobbers}
